Molecular Gas \old{Dynamics} \new{Kinematics} of the Strongly-lensed Quasar Host Galaxy RXS J1131$-$1231

### 2016-11-22 WRITEUP/diff.tex
incoporated DR's comments, diff between submitted and latest (assuming ready to be re-submitted)

\begin{abstract}
We report observations of \bco and \cco line emission towards
the quadruply-lensed quasar
RXS\,J1131$-$1231 at $z$\,=\,0.654 obtained using the
\pdbi (PdBI) and the \carma (CARMA).
Our lens modeling shows that the asymmetry in the double-horned \bco line profile
is mainly a result of differential lensing, where
the magnification factor varies from $\sim$3 to $\sim$9 across
different kinematic components.
The intrinsically symmetric line profile with a conspicuous source-plane velocity
gradient suggests that
the host galaxy is an extended rotating disk, with a CO size of $R_{\rm CO}$$\sim$6\,kpc and
a dynamical mass of $M_{\rm dyn}$\ssim8\E{10}\,\Msun.
In addition, we find a secondary CO-emitting source near RXS\,J1131$-$1231 whose location is
consistent with the optically-faint companion reported in previous studies.
The lensing-corrected molecular gas masses are $M_{\rm gas}$\ssim1.4\E{10}\,\Msun
and \ssim2\E{9}\,\Msun for RXS\,J1131$-$1231 and the companion, respectively.
The gas mass fraction of \old{$\sim$19\% } \new{$\sim$18\%} inferred for RXS\,J1131$-$1231 is consistent with the trend of decreasing molecular gas fraction since $z$\ssim2 reported in recent studies.
We find lensing-corrected stellar and dust masses, an IR luminosity, and a
star formation rate of
$M_{*}$\ssim3\E{10}\,\Msun, $M_{\rm dust}$\ssim\old{4}\new{3}\E{8}\,\Msun, $L_{\rm IR}$\ssim1.5\E{12}\,\Lsun,  and SFR$_{\rm FIR}$\ssim120\,\sfrU for RXS\,J1131$-$1231.
The source-plane morphologies of its gas and stellar populations
indicate that the star-formation activity may be as extended as the molecular gas reservoir.
We find a $M_{\rm BH}$$/$$M_{\rm bulge}$ ratio of \old{\mbox{$>$0.27\petm{11}{8}\%}} \new{$>$0.27\petm{0.11}{0.08}\%} which is higher
than the
local value, suggesting that the bulk of the black hole mass of RXSJ1131-1231 is largely in place while its stellar bulge is still assembling.
\end{abstract}

@@

%--------------------------------------------------------------------------
%                          Observations details
%--------------------------------------------------------------------------
\section{Observations} \label{sec:obs}
\subsection{PdBI \bco}
Observations of the \bco rotational line
($\nu_{\rm rest}$\,=\,$230.53800$ GHz)
\old{at the $\nu_{\rm LO}$\eq139.256\,GHz}
\new{at the tuning frequency of $\nu_{\rm obs}$\eq139.256\,GHz}
% redshifted to $\nu_{\rm obs}$\eq139.40739\,GHz
were carried out using IRAM \pdbi (PdBI; Program ID: S14BX; PI: D.
Riechers). Two observing runs were carried out on 2014 December 06 and 2015
February 05 under good weather conditions in the C and D array configurations,
respectively.
This resulted in 3.75 hours of cumulative six antenna-equivalent on-source
 time after discarding unusable visibility data.
The 2 mm receivers were used to cover the redshifted \bco line
and the underlying continuum emission, employing a correlator setup that provides
an effective bandwidth of 3.6 GHz (dual polarization) and a native spectral resolution of 1.95\,MHz
($\sim$\,$4.2$\,\kms).
The nearby quasars B1127$-$145 and B1124$-$186 were observed every 22 minutes
for pointing, secondary amplitude, and phase calibration, and B1055$+$018 was
observed as the bandpass calibrator for both tracks.
MWC349 and 3C279 were observed as primary flux calibrators for the C and D
array observations, respectively, yielding calibration accuracy better than 15\%.

\subsection{CARMA \cco}
Observations of the \cco rotational line in RXJ1131 \old{($\nu_{\rm rest}$\,=\,345.79599\,GHz) redshifted to $\nu_{\rm obs}$\eq209.10443\,GHz}
\new{($\nu_{\rm rest}$\,=\,345.79599\,GHz)
% redshifted to
at the observe frequency of $\nu_{\rm obs}$\eq209.10443\,GHz}    % i.e. where we thought the line was redshifted to
were carried out with the \carma (CARMA;
Program ID: cf0098; PI: D. Riechers)
in the D array configuration on 2014 February 02 under poor 1.5\,mm
weather conditions and on 2014 February 17 under good 1.5\,mm
weather conditions.
This resulted in a total on-source time of 2.94 hours after flagging poor
visibility data.
The correlator setup provides a bandwidth of 3.75 GHz in
each sideband and a %native
spectral resolution of 12.5 MHz ($\sim$17.9 \kms). The
line was placed in the lower sideband with the local oscillator tuned to $\nu_{\rm LO}\sim$216 GHz. The radio quasars J1127$-$189 (first track) and 3C273
(second track) were observed
every 15 minutes for pointing, amplitude, and phase calibration. Mars was
observed as the primary absolute flux calibrator and 3C279 was observed as
the bandpass calibrator for both tracks.

@@

@@

%--------------------------------------------------------------------------
%                                Results
%--------------------------------------------------------------------------
\section{Results} \label{sec:results}
\new{The observed properties of \bco and \cco emission are summarized in \Tab{obsprop}.}
\input{table_obsprop}

\subsection{\bco Emission} \label{sec:CO21}
We detect \bco line emission toward the background source in the PdBI data
at $\gtrsim$\,27$\sigma$ significance, \old{confirming the redshift at $z_{\rm CO}$\eq0.6537\,$\pm$\,0.0005.} \new{enabling us to constrain its redshift at
$z_{\rm CO}$\eq0.6541\,$\pm$\,0.0002\mbox{\footnote{This redshift is derived by fitting a double-Gaussian to
the de-lensed spectrum, which is shown in \Fig{delensed}}.}}
\old{The emission is spatially and dynamically resolved} \new{The emission is spatially and kinematically resolved}
with a highly asymmetric double-horned line profile
as shown in \mbox{\Fig{CO21spec}}. Fitting a double Gaussian results in peak
flux densities of 75.3\pmm2.6 mJy and 24.0\pmm2.0 mJy, and a FWHM of
179\pmm9 \kms and 255\pmm28 \kms for the two components, respectively. The peaks are separated by
$\Delta v_{\rm sep}$\eq400\pmm12\,\kms. The total integrated line flux is \old{24.1\,$\pm$\,2.3 Jy \kms} \new{20.3\,$\pm$\,0.6 Jy \kms}. % see 15May16/

\begin{figure}[htbp]
\centering
\includegraphics[width=0.45\textwidth]{../Figures/SpecCO21_twinx.eps}
\caption{Continuum-subtracted spectrum (histogram) of \bco emission towards RXJ1131, with a spectral resolution of
21.5\,\kms. The solid black line shows a double-Gaussian fit to the line profile.
The velocity scale is with respect to \old{$z$\,=\,0.6537, which is approximately the line center considering the asymmetry resulting from differential lensing.} \new{$z$\,=\,0.6541, which corresponds to the line center of RXJ1131 based on
the de-lensed line profile (\Fig{delensed})}.
A detailed discussion of this effect is presented in \Sec{differential}. \label{fig:CO21spec}}
\end{figure}
\vspace{.2em}
% moment 0 map, highest SNR: CASA chan=125~159 <=> GILDAS 126-160 <=> python 125-160
% - sigma = 0.305 Jy km/s/Beam
%   - note that theoretical sigma is lower = 1.5 * sqrt(160-126+1) * 21.5 ~ 0.2 Jy km/s /beam, due to higher noise in some channels with emission
We construct a zeroth order moment map, red/blue channel maps, and
first and second moment maps, as shown in \Fig{CO21mom},
using the $uv$-continuum subtracted data cube over a velocity range of
$\Delta v$ $\sim$ 750\,\kms.
The higher-order moment maps are produced using
unbinned channel maps with 3$\sigma$ clipping.
The peak flux density is 8.12\pmm0.30 Jy\,\kms\,beam\pmOne
in the intensity map.

\old{
The deconvolved source size FWHM obtained by fitting a two-dimensional Gaussian to the integrated line map in
the image plane
is 5\farcs1\pmm0\farcs72 $\times$ 3\farcs72\pmm0\farcs66,
and thus, the emission is resolved over $\sim$2.2 beams.
While the lensed emission is not strictly distributed as a two-dimensional
Gaussian;
the fit recovers the line intensity enclosed by the emitting
region, therefore we take this as an estimate on the full extent of the lensed
emission. On the other hand, if we assume that the spatial distribution of
the lensed molecular gas emission is similar to that in the optical to \mbox{\nir}
wavelengths, the lensed emission would be more accurately described by an
annulus, enclosing the partially complete ``Einstein ring'' and}
\old{\mbox{the lensed knots (see \Fig{CO21mom}).}}
\new{The deconvolved source size FWHM from fitting a single two-dimensional Gaussian
to the integrated line image yields 5\farcs1\pmm0\farcs7$\times$3\farcs7\pmm0\farcs7,
consistent with the results obtained by $uv$-plane fitting within the uncertainties.
% UV plane: E_GAUSS: 4.5 +/- 0.1 x 3.5 +/- 0.2
To model the complex spatial distribution of the line emission (\Fig{CO21mom}), we
fit two independent Gaussians and find deconvolved source sizes of
3\farcs8\pmm0\farcs4$\times$1\farcs9\pmm0\farcs4 and 3\farcs6\pmm0\farcs3$\times$1\farcs5\pmm0\farcs3.
Therefore, the emission is slightly resolved over $\sim$\,2 beams.
The lensed CO emission is unlikely to be distributed as Gaussians
given the morphology seen in optical and \nir emission that were observed at higher resolution,
i.e., the lensed emission of CO (without beam convolution) is more likely to have
an annulus configuration enclosing a partially complete ``Einstein ring'' with
structures along the arc
and knots (see \Fig{CO21mom}). Nevertheless, the deconvolved source sizes and the
spatially offset blue wing compared to optical emission suggest that
the CO-emitting region in RXJ1131 is more extended than its stellar (and of course quasar) emission.}

@@

\subsection{\cco Emission}
We detect \cco line emission towards RXJ1131 in the CARMA data at $\gtrsim$\,5$\sigma$ significance.
The spectrum is shown in \Fig{co32spec} and appears to be consistent with a
double-peaked profile. We estimate a line intensity of
\old{35.7\,$\pm$\,21.9 Jy\,\kms} \new{35.7\,$\pm$\,6.9\,Jy\,\kms} by summing up fluxes over the FWZI
linewidth used to infer the \bco line intensity ($\sim$700 \kms).
Assuming the spatial extent of \bco and \cco is similar and therefore the emission is
magnified by the same amount, the measured line intensities
correspond to a brightness temperature ratio of
$r_{\rm 32}$\,=\,$T_{\small \cco}$$/$$T_{\small \bco}$\,=\,\old{0.66\,$\pm$\,0.41. Taking into account the large phase errors associated with \cco, this is consistent with}
\new{0.78\,$\pm$\,0.62, where this uncertainty includes
those introduced in absolute flux calibration and is dominated by
the large phase errors associated with the \cco observations.
This ratio is consistent with}
thermalized excitation within the uncertainties, as commonly observed in nuclear regions of
nearby ULIRGs and high-$z$ quasars \citep[e.g.,][]{Weiss07a, CW13}, but also
with the lower excitation seen in normal star-forming disks \citep[e.g.,][]{Dannerbauer09a, CW13}.
% see DANNERBAUER09 intro
% i.e., we cannot rule out the possibility that this guy is similar to gal. pop. of either SF modes.

\begin{figure}[!htbp]
%\centering
\includegraphics[width=0.455\textwidth]{../Figures/coOverlay.eps}
\caption{CARMA \cco line profile (solid) without continuum subtraction is
over-plotted on the continuum-subtracted PdBI \bco line profile (dashed).
The velocity scale is with respect to \old{\mbox{$z$=0.6537, which corresponds to the
dynamical center of the \bco line.}} \new{\mbox{$z$=0.6541, which corresponds to the
line center of \bco line emission.}} The spectral resolution for \cco and \bco
is 35.8 \kms and 21.5 \kms, respectively.
 \label{fig:co32spec}}
\end{figure}

@@

We detect \old{2\,mm} \new{2.2\,mm} continuum emission at an
 integrated flux density of
1.2\pmm0.2 mJy, with a peak flux of
$S_{\nu}$\,=\,799\pmm88\,$\mu$Jy\,beam\pmOne
centered on the lensing galaxy (\Fig{cont}).
\new{We note that the reported flux uncertainties do not include those from absolute flux calibration.}
Slightly extended emission
along the lensed arc is also detected.
This suggests that we detect emission in both
the foreground galaxy and the background galaxy and that the
emission is marginally resolved along its major axis.
We subtract a point source model in the $uv$-plane to remove the unresolved part of the
emission, which we here assume to be dominated by the foreground galaxy. The peak emission
\old{(0.39\,$\pm$\,0.08\,mJy)}
\new{of flux $S_{\nu}$\eq0.39\,$\pm$\,0.08\,mJy}
in the residual map coincides with the lensed arc, and is consistent with
the difference between the integrated and the peak flux in the
original continuum map ($\sim$0.4 mJy).
We therefore adopt \old{$S_{\nu}$ = 0.39\pmm0.08 mJy} \new{$S_{\nu}$\eq0.39\pmm0.22 mJy} as the 2\,mm continuum flux measurement for
the background galaxy (RXJ1131).
\old{The quoted uncertainty is from the flux measurement in the residual map, }
\new{The quoted uncertainty is solely based on the uncertainties associated with the flux density of the
point source model ($\delta S_{\nu}$\eq0.088\,mJy) and
that of the integrated flux in the original data (0.2\,mJy), }and does not account for that in the
de-blending procedure, where we have assigned 100\% of the point source flux to the foreground galaxy.
We report the peak flux in the original map
($S_{\nu}$\,=\,799\pmm88\,$\mu$Jy\,beam\pmOne) for the foreground galaxy, which
is the best estimate possible at the resolution of our observations, but we acknowledge that a non-negligible contribution from the background source to the peak flux cannot be ruled out.
% The quote uncertainty on the flux density of the foreground galaxy based on the peak flux density
% assumes that the foreground galaxy is a point source, the...

\begin{figure}[!htbp]
%\centering
\includegraphics[trim=12 27 0 1, clip, width=0.475\textwidth]{../Figures/F555W_ContPdBI.eps}
\includegraphics[trim=10 5 0 0, clip, width=0.4695\textwidth]{../Figures/F555W_ContVLA.eps}
\caption{Top: overlay of the 2\,mm continuum emission on the optical image.
Contours start and increment at steps of
$\pm$3$\sigma$, where $\sigma_{\rm 2mm}$\,=\,0.082 mJy beam\pmOne.
Bottom: overlap of the VLA 5\,GHz continuum emission on the optical image.
\new{Contours correspond to [10, 40, 60, 100]\%$\times$ the peak flux density of $S_{\rm 5GHz}$\eq0.74\pmm0.01 mJy.}
% Radio emission towards the foreground radio core is detected at $\gtrsim$57$\sigma$,
% where $\sigma_{\rm 5GHz}$\,=\,13 $\mu$Jy beam\pmOne.
The central crosses in both panels indicate the centroid of the foreground galaxy,
as detected in the optical image.
The synthesis beam size is 4\farcs4 $\times$ 2\farcs0, at PA = 13$\degr$ for
the PdBI observations (top), and
0\farcs5 $\times$ 0\farcs4 (PA = 0.18$\degr$) for
the VLA observations (bottom).
\label{fig:cont}}\vspace{0.51em}
\end{figure}

The VLA C-band continuum image in \Fig{cont} shows resolved emission from the
jets and the core of the foreground elliptical galaxy
as well as emission toward the background quasar.
Multiple peaks are seen along the arc with their centroids
coincident with the optical emission from the quasar.
We extract the flux densities for the lensing arc and the radio core in \Tab{photometry}.
We find a spectral index of $\alpha^{\rm 2mm}_{\rm 6cm}$\,=\,$-$\old{0.024}\new{0.02}
for the foreground galaxy and $\alpha^{\rm 2mm}_{\rm 6cm}$\,=\,$-$\old{0.345}\new{0.35}
for the background galaxy by fitting
power-laws ($S_\nu \propto \nu^{\alpha}$) to their continuum emission at
5\,GHz and 2\,mm.
\new{The spectral slope derived for the background source is flatter than the typical slope of pure synchrotron emission ($\alpha$\ssim$-$0.7), suggesting
that a dominant fraction of the observed 2\,mm emission arises from cold dust and free-free emission.
% that the 2\,mm emission is dominated by non-synchrotron emission.
This spectral slope would only be shallower
if a non-negligible fraction from the background source
contribute to the point source flux at 2\,mm in the deblending process. This would also
explain the atypical flat spectrum found for the foreground galaxy.
Assuming a synchrotron slope of $\alpha$\ssim$-$0.7 and that the emission at 5\,GHz is purely synchrotron,
we find $S_{\rm 2mm}$\eq0.27\pmm0.22\,mJy from cold dust and free-free emission in the background galaxy. }

@@

\begin{figure*}[!htbp]
\centering
\includegraphics[width=1.0\textwidth]{../Figures/co_channel_maps.eps}
\caption{
Channel maps of the PdBI \bco data cube toward RXJ1131 at 21.5\,\kms resolution.
Black crosses indicate the positions of the lensed knots (AGN emission,
which correspond to components ABCD in \citetalias{Claeskens06a}). The central white-filled
star indicates the position of the foreground lensing galaxy (component G
in \citetalias{Claeskens06a}).
Central velocities are shown at the top of each map.
Contours start and increment at steps of
$\pm$3$\sigma$. The beam is denoted in the bottom right panel. \label{fig:chanmap}}
\end{figure*}

>>>>

\begin{abstract}
We report observations of \bco and \cco line emission towards
the quadruply-lensed quasar
RXS\,J1131$-$1231 at $z$\,=\,0.654 obtained using the
\pdbi (PdBI) and the \carma (CARMA).
Our lens modeling shows that the asymmetry in the double-horned \bco line profile
is mainly a result of differential lensing, where
the magnification factor varies from $\sim$3 to $\sim$9 across
different kinematic components.
The intrinsically symmetric line profile with a conspicuous source-plane velocity
gradient suggests that
the host galaxy is an extended rotating disk, with a CO size of $R_{\rm CO}$$\sim$6\,kpc and
a dynamical mass of $M_{\rm dyn}$\ssim8\E{10}\,\Msun.
In addition, we find a secondary CO-emitting source near RXS\,J1131$-$1231 whose location is
consistent with the optically-faint companion reported in previous studies.
The lensing-corrected molecular gas masses are $M_{\rm gas}$\eq(1.4\pmm0.3)\E{10}\,\Msun
and \eq(2.0\pmm0.1)\E{9}\,\Msun for RXS\,J1131$-$1231 and the companion, respectively.
The gas mass fraction of \old{$\sim$19\% } \new{$\sim$18\pmm4\%} inferred for RXS\,J1131$-$1231 is consistent with the trend of decreasing molecular gas fraction since $z$\ssim2 reported in recent studies.
We find lensing-corrected stellar and dust masses, an IR luminosity, and a
star formation rate of
$M_{*}$\eq(3\pmm1)\E{10}\,\Msun, $M_{\rm dust}$\ssim\old{4}\new{3}\E{8}\,\Msun, $L_{\rm IR}$\ssim1.5\E{12}\,\Lsun,  and SFR$_{\rm FIR}$\eq(120\pmm63)\,\sfrU for RXS\,J1131$-$1231.
The source-plane morphologies of its gas and stellar populations
indicate that the star-formation activity may be as extended as the molecular gas reservoir.
We find a $M_{\rm BH}$$/$$M_{\rm bulge}$ ratio of \old{\mbox{$>$0.27\petm{11}{8}\%}} \new{$>$0.27\petm{0.11}{0.08}\%} which is higher
than the
local value, suggesting that the bulk of the black hole mass of RXSJ1131-1231 is largely in place while its stellar bulge is still assembling.
\end{abstract}

@@

%--------------------------------------------------------------------------
%                          Observations details
%--------------------------------------------------------------------------
\section{Observations} \label{sec:obs}
\subsection{CARMA \cco}
Observations of the \cco rotational line \old{in RXJ1131} ($\nu_{\rm rest}$\,=\,345.79599\,GHz) redshifted to $\nu_{\rm obs}$\eq209.10443\,GHz \new{towards RXJ1131 at $z_{\rm QSO}$\eq0.658}
were carried out with the \carma (CARMA;
Program ID: cf0098; PI: D. Riechers)
in the D array configuration\new{. They were carried out} on 2014 February 02 under poor 1.5\,mm
weather conditions and on 2014 February 17 under good 1.5\,mm
weather conditions.
This resulted in a total on-source time of 2.94 hours after flagging poor
visibility data.
The correlator setup provides a bandwidth of 3.75 GHz in
each sideband and a %native
spectral resolution of 12.5 MHz ($\sim$17.9 \kms). The
line was placed in the lower sideband with the local oscillator tuned to $\nu_{\rm LO}\sim$216 GHz. The radio quasars J1127$-$189 (first track) and 3C273
(second track) were observed
every 15 minutes for pointing, amplitude, and phase calibration. Mars was
observed as the primary absolute flux calibrator and 3C279 was observed as
the bandpass calibrator for both tracks.

@@

\subsection{PdBI \bco}
Observations of the \bco rotational line
($\nu_{\rm rest}$\,=\,$230.53800$ GHz)
\old{at the $\nu_{\rm LO}$\eq139.256\,GHz}
\new{redshifted to $\nu_{\rm obs}$\eq139.256\,GHz towards RXJ1131 at the CARMA \cco redshift of 
$z_{\rm CO(3-2)}$\eq0.655}
were carried out using IRAM \pdbi (PdBI; Program ID: S14BX; PI: D.
Riechers). Two observing runs were carried out on 2014 December 06 and 2015
February 05 under good weather conditions in the C and D array configurations,
respectively.
This resulted in 3.75 hours of cumulative six antenna-equivalent on-source
 time after discarding unusable visibility data.
The 2 mm receivers were used to cover the redshifted \bco line
and the underlying continuum emission, employing a correlator setup that provides
an effective bandwidth of 3.6 GHz (dual polarization) and a native spectral resolution of 1.95\,MHz
($\sim$\,$4.2$\,\kms).
The nearby quasars B1127$-$145 and B1124$-$186 were observed every 22 minutes
for pointing, secondary amplitude, and phase calibration, and B1055$+$018 was
observed as the bandpass calibrator for both tracks.
MWC349 and 3C279 were observed as primary flux calibrators for the C and D
array observations, respectively, yielding calibration accuracy better than 15\%.

@@

%--------------------------------------------------------------------------
%                                Results
%--------------------------------------------------------------------------
\section{Results} \label{sec:results}
\input{table_obsprop}

\subsection{\bco Emission} \label{sec:CO21}
We detect \bco line emission toward the background source in the PdBI data
at $\gtrsim$\,27$\sigma$ \old{significance, confirming} \new{significance. Based on this measurement, we refine} the redshift \old{at} \new{of RXJ1131 to} \old{$z_{\rm CO}$\eq0.6537\,$\pm$\,0.0005.}
\new{$z_{\rm CO}$\eq0.6541\,$\pm$\,0.0002\mbox{\footnote{This redshift is derived by fitting a double-Gaussian to
the de-lensed spectrum, which is shown in \Fig{delensed}
instead of the observed spectrum (\Fig{CO21spec}) to avoid biases in our 
redshift determination 
due to differential lensing (see \Sec{differential})}.}}
\old{The emission is spatially and dynamically resolved} \new{The emission is spatially and kinematically resolved}
with a highly asymmetric double-horned line profile
as shown in \Fig{CO21spec}. Fitting a double Gaussian results in peak
flux densities of 75.3\pmm2.6 mJy and 24.0\pmm2.0 mJy, and a FWHM of
179\pmm9 \kms and 255\pmm28 \kms for the two components, respectively. The peaks are separated by
$\Delta v_{\rm sep}$\eq400\pmm12\,\kms. The total integrated line flux is \old{24.1\,$\pm$\,2.3 Jy \kms} \new{20.3\,$\pm$\,0.6 Jy \kms}. % see 15May16/

\begin{figure}[htbp]
\centering
\includegraphics[width=0.45\textwidth]{../Figures/SpecCO21_twinx.eps}
\caption{Continuum-subtracted spectrum (histogram) of \bco emission towards RXJ1131, with a spectral resolution of
22\,\kms. The solid black line shows a double-Gaussian fit to the line profile.
The velocity scale is with respect to \old{$z$\,=\,0.6537, which is approximately the line center considering the asymmetry resulting from differential lensing.} \new{$z$\,=\,0.6541, which corresponds to the line center of RXJ1131 based on
the de-lensed line profile (\Fig{delensed})}.
A detailed discussion of this effect is presented in \Sec{differential}. \label{fig:CO21spec}}
\end{figure}
\vspace{.2em}
% moment 0 map, highest SNR: CASA chan=125~159 <=> GILDAS 126-160 <=> python 125-160
% - sigma = 0.305 Jy km/s/Beam
%   - note that theoretical sigma is lower = 1.5 * sqrt(160-126+1) * 21.5 ~ 0.2 Jy km/s /beam, due to higher noise in some channels with emission
We construct a zeroth order moment map, red/blue channel maps, and
first and second moment maps, as shown in \Fig{CO21mom},
using the $uv$-continuum subtracted data cube over a velocity range of
$\Delta v$ $\sim$ 750\,\kms.
The higher-order moment maps are produced using
unbinned channel maps with 3$\sigma$ clipping.
The peak flux density is 8.12\pmm0.30 Jy\,\kms\,beam\pmOne
in the intensity map.

\old{
The deconvolved source size FWHM obtained by fitting a two-dimensional Gaussian to the integrated line map in
the image plane
is 5\farcs1\pmm0\farcs72 $\times$ 3\farcs72\pmm0\farcs66,
and thus, the emission is resolved over $\sim$2.2 beams.
While the lensed emission is not strictly distributed as a two-dimensional
Gaussian;
the fit recovers the line intensity enclosed by the emitting
region, therefore we take this as an estimate on the full extent of the lensed
emission. On the other hand, if we assume that the spatial distribution of
the lensed molecular gas emission is similar to that in the optical to \mbox{\nir}
wavelengths, the lensed emission would be more accurately described by an
annulus, enclosing the partially complete ``Einstein ring'' and}
\old{\mbox{the lensed knots (see \Fig{CO21mom}).}}
\new{The deconvolved source size FWHM from fitting a single two-dimensional Gaussian 
to the integrated line image yields 5\farcs1\pmm0\farcs7$\times$3\farcs7\pmm0\farcs7,  % In the image plane, the *convolved* size is 6.6"+/-0.5" x 4.5"+/-0.3". 
consistent with that obtained by $uv$-plane fitting within the uncertainties. 
% UV plane: E_GAUSS: 4.5 +/- 0.1 x 3.5 +/- 0.2
The spatial distribution of the observed CO emission is unlikely to be fully 
encapsulated by a simple Gaussian 
given its skewed emission, which also appears to be a superposition of two components (\Fig{CO21mom}). 
% To better capture the spatial distribution of the line emission, we 
We therefore also fit a model of two Gaussians which yeilds deconvolved source sizes of 
3\farcs8\pmm0\farcs4$\times$1\farcs9\pmm0\farcs4 and 3\farcs6\pmm0\farcs3$\times$1\farcs5\pmm0\farcs3, respectively.
The deconvolved source size together with
% complex morphology of a partial ``Einstein ring'' with 
% structures along the arc and knots 
% seen in optical and \nir emission (see \Fig{CO21mom}). %that were observed at higher resolution, 
the spatially more extended blue wing compared to the optical 
``Einstein ring" of diameter $\sim$3\farcs6 (top right panel of \Fig{CO21mom}) suggest that 
the CO-emitting region in RXJ1131 is more extended than its stellar and quasar emission.}

@@

\subsection{\cco Emission}
We detect \cco line emission towards RXJ1131 in the CARMA data at $\gtrsim$\,5$\sigma$ significance.
\old{The spectrum is shown in \mbox{\Fig{co32spec}} and appears to be consistent with a
double-peaked profile. }
\new{The \cco spectrum appears to be consistent with a double-peaked profile, as shown in \Fig{co32spec}, where we over-plot spectra of the \bco and \cco lines.}
\new{We extract the peak fluxes and their corresponding uncertainties for the blue and red wing independently.
We find a peak line flux of 5.13\pmm1.43 Jy\,\kms beam\pmOne for the blue wing, 
indicating a $\gtrsim$3$\sigma$ detection for this component, and a peak line 
flux of 11.45\pmm1.99\,Jy\,\kms beam\pmOne for the red wing, indicating a $\sim$\,6$\sigma$ detection. 
}
We estimate a line intensity of
\old{35.7\,$\pm$\,21.9 Jy\,\kms} \new{35.7\,$\pm$\,6.9\,Jy\,\kms (\Tab{obsprop})} by summing up fluxes over the FWZI
linewidth used to infer the \bco line intensity ($\sim$700 \kms).

Assuming the spatial extent of \bco and \cco is similar and therefore the emission is
magnified by the same amount, the measured line intensities
correspond to a brightness temperature ratio of
$r_{\rm 32}$\,=\,$T_{\small \cco}$$/$$T_{\small \bco}$\,=\,\old{0.66\,$\pm$\,0.41. Taking into account the large phase errors associated with \cco, this is consistent with}
\new{0.78\,$\pm$\,0.37, where this uncertainty includes
the uncertainties in absolute flux calibration.
This ratio is consistent with}
thermalized excitation within the uncertainties, as commonly observed in nuclear regions of
nearby ULIRGs and high-$z$ quasars \citep[e.g.,][]{Weiss07a, CW13}, but also
with the lower excitation seen in normal star-forming disks \citep[e.g.,][]{Dannerbauer09a, CW13}.
% see DANNERBAUER09 intro
% i.e., we cannot rule out the possibility that this guy is similar to gal. pop. of either SF modes.

\begin{figure}[!htbp]
%\centering
\includegraphics[width=0.455\textwidth]{../Figures/coOverlay.eps}
\caption{CARMA \cco line profile (solid) without continuum subtraction is
over-plotted on the continuum-subtracted PdBI \bco line profile (dashed).
The velocity scale is \old{with respect to \mbox{$z$=0.6537, which corresponds to the
dynamical center of the \bco line.}} \new{same as in \Fig{CO21spec}).} The spectral resolution for \cco and \bco
is 36 \kms and 22 \kms, respectively.
 \label{fig:co32spec}}
\end{figure}

@@

We detect \old{2\,mm} \new{2.2\,mm} continuum emission at an
 integrated flux density of
1.2\pmm0.2 mJy, with a peak flux of
$S_{\nu}$\,=\,799\pmm88\,$\mu$Jy\,beam\pmOne
centered on the lensing galaxy (\Fig{cont}).
Slightly extended emission
along the lensed arc is also detected.
This suggests that we detect emission in both
the foreground and the background galaxy and that the
emission is marginally resolved along its major axis.
We subtract a point source model in the $uv$-plane to remove the unresolved part of the
emission, which we here assume to be dominated by the foreground galaxy. The peak 
\old{flux (0.39\,$\pm$\,0.08\,mJy)}
\new{emission}
in the residual map coincides with the lensed arc, \old{and} \new{with 
a flux density of $S_{\nu}$\eq0.39\,$\pm$\,0.08\,mJy.}
\new{This peak flux} is consistent with
the difference between the integrated and the peak flux in the
original continuum map ($\sim$0.4 mJy).
We therefore adopt \old{$S_{\nu}$ = 0.39\pmm0.08 mJy} \new{$S_{\nu}$\eq0.39\pmm0.12 mJy} as the 2\,mm continuum \old{emission towards} \new{flux measurement for}
the background galaxy (RXJ1131).
The quoted uncertainty is \old{from the flux measurement in the residual map, }
\new{derived by adding those associated with the flux density of the
point-source model ($\delta S_{\nu}$\eq0.088\,mJy) and the peak flux in the residual map (0.08 mJy) in 
quadrature,}
and does not account for that in the
de-blending procedure, where we have assigned 100\% of the point source flux to the foreground galaxy.
We report the peak flux in the original map
($S_{\nu}$\,=\,799\pmm88\,$\mu$Jy\,beam\pmOne) for the foreground galaxy, which
is the best estimate possible at the resolution of our observations, but we acknowledge that a non-negligible contribution from the background source to the peak flux cannot be ruled out.

\begin{figure}[!htbp]
%\centering
\includegraphics[trim=12 27 0 1, clip, width=0.475\textwidth]{../Figures/F555W_ContPdBI.eps}
\includegraphics[trim=10 5 0 0, clip, width=0.4695\textwidth]{../Figures/F555W_ContVLA.eps}
\caption{Top: overlay of the PdBI 2\,mm continuum emission on the optical image.
Contours start and increment at steps of
$\pm$3$\sigma$, where $\sigma_{\rm 2mm}$\,=\,0.082 mJy beam\pmOne.
Bottom: overlap of the VLA 5\,GHz continuum emission on the optical image.
\new{Contours correspond to $\pm2^n\sigma$, where $\sigma_{\rm 5GHz}$\,=\,13 $\mu$Jy beam\pmOne
and $n$ is an integer starting from 2 to 5.
Radio emission towards the foreground radio core is detected at $\gtrsim$57$\sigma$.}
The central crosses in both panels indicate the centroid of the foreground galaxy,
as detected in the optical image.
The synthesis beam size is 4\farcs4 $\times$ 2\farcs0, at PA = 13$\degr$ for
the PdBI observations (top), and
0\farcs5 $\times$ 0\farcs4 (PA = 0.18$\degr$) for
the VLA observations (bottom).
\label{fig:cont}}\vspace{0.51em}
\end{figure}

The VLA C-band continuum image in \Fig{cont} shows resolved emission from the
jets and the core of the foreground elliptical galaxy
as well as emission toward the background quasar.
Multiple peaks are seen along the arc with their centroids
coincident with the optical emission from the quasar.
We extract the flux densities for the lensing arc and the radio core in \Tab{photometry}.
We find a spectral index of $\alpha^{\rm 2mm}_{\rm 6cm}$\,=\,$-$\old{0.024}\new{0.02\pmm0.07}
for the foreground galaxy and $\alpha^{\rm 2mm}_{\rm 6cm}$\,=\,$-$\old{0.345}\new{0.35\pmm0.21}
for the background galaxy by fitting
power-laws ($S_\nu \propto \nu^{\alpha}$) to their continuum emission at
5\,GHz and 2\,mm.
\new{The spectral slope derived for the background source is flatter than the typical slope of pure synchrotron emission \mbox{\citep[$\alpha$\ssim$-$0.7; ][]{Andreani93a}}, suggesting 
that a fraction of the observed 2\,mm emission arises from thermal dust and free-free emission. 
This spectral slope would be even shallower 
if the background source has a contribution in the
2\,mm flux of the point-source model used
in the deblending process. This would also 
explain the flat spectrum found for the foreground galaxy that is atypical of elliptical galaxies. 
Assuming a synchrotron slope of $\alpha$\ssim$-$0.7, we find
a flux density of $S_{\rm 2mm}$\eq0.122\pmm0.004 mJy at 2\,mm      % (139.256/4.8815)**-0.7 *1.273 = 0.122; error: 1.273 +/- 0.042 --> 0.042/1.273 * 0.122 = 0.004
for the background source based on its 5\,GHz flux,
and thus a flux excess of $S_{\rm 2mm}$\eq0.27\pmm0.08\,mJy that arises from thermal dust emission.}

@@

\begin{figure*}[!htbp]
\centering
\includegraphics[width=1.0\textwidth]{../Figures/co_channel_maps.eps}
\caption{
Channel maps of the PdBI \bco data cube toward RXJ1131 at 22\,\kms resolution.
Black crosses indicate the positions of the lensed knots (AGN emission,
which correspond to components ABCD in \citetalias{Claeskens06a}). The central white-filled
star indicates the position of the foreground lensing galaxy (component G
in \citetalias{Claeskens06a}).
Central velocities are shown at the top of each map.
Contours start and increment at steps of
$\pm$3$\sigma$. The beam is denoted in the bottom right panel. \label{fig:chanmap}}
\end{figure*}
